### 2013-12-08 results.tex
added matlab syntax to generate Rsq for axis fits to input into LaTeX doc

Measurements of the prostate total and CG dimensions along the three standard
anatomic axes (apex-to-base, lateral-to-lateral, and anterior-to-posterior)
were made (Table~\ref{tab:mr_arfi_axes}), and the correlation between the
imaging axis measurements was analyzed (Figure~\ref{fig:mr_arfi_path_axes}).
ARFI was most correlated to MR in the lateral-to-lateral axis in both the total
and CG (R$^2$ = 0.57 and 0.32, respectively), with mean overestimates of 13.5
$\pm$ 11.0\% and 11.5 $\pm$ 22.5\%, respectively
(Table~\ref{tab:mr_arfi_axes_error}).  ARFI had moderate correlation with the
total prostate gland and CG axes in the anterior-to-posterior dimension (R$^2$
= 0.23 and R$^2$ = 0.34), respectively, with overestimates of 5.7 $\pm$ 20.6
and -6.1 $\pm$ 21.1\%.  ARFI imaging had weak correlation with MR images in the
apex-to-base dimension (R$^2$ = 0.19, total gland and R$^2$ = 0.09, CG), with
differences of 2.4 $\pm$ 17.0 and 1.2 $\pm$ 19.8\%, respectively.

>>>>

Measurements of the prostate total and CG dimensions along the three standard
anatomic axes (apex-to-base, lateral-to-lateral, and anterior-to-posterior)
were made (Table~\ref{tab:mr_arfi_axes}), and the correlation between the
imaging axis measurements was analyzed (Figure~\ref{fig:mr_arfi_path_axes}).
ARFI was most correlated to MR in the lateral-to-lateral axis in both the total
and CG (R$^2$ = \totalLatLatRsq and \centralLatLatRsq, respectively), with mean overestimates of 13.5
$\pm$ 11.0\% and 11.5 $\pm$ 22.5\%, respectively
(Table~\ref{tab:mr_arfi_axes_error}).  ARFI had moderate correlation with the
total prostate gland and CG axes in the anterior-to-posterior dimension (R$^2$
= \totalAntPostRsq and \centralAntPostRsq), respectively, with overestimates of 5.7 $\pm$ 20.6
and -6.1 $\pm$ 21.1\%.  ARFI imaging had weak correlation with MR images in the
apex-to-base dimension (R$^2$ = \totalApexBaseRsq, total gland and R$^2$ = \centralApexBaseRsq, central gland), with
differences of 2.4 $\pm$ 17.0 and 1.2 $\pm$ 19.8\%, respectively.
